Global adjoint tomography -- Model GLAD-M25 \\ Supplementary Material

### 2020-02-23 main.tex
Updates from Overleaf

Construction of the first seismic tomographic models of the Earth dates back to the late 1970s~\citep{Aki77,Dziewonski77,SenTok77} and early 1980s~\citep[e.g.,][]{WD84,Nataf1984}.
Around the same time,
\cite{BaChLa77}, \cite{Lailly1983}, and~\cite{Tar84} formulated and adapted the theory of adjoint-state methods~\citep{Chavent1974} for exploration seismology with the goal of capturing the full physics of seismic wave propagation.
Mainly due to computational challenges,
it took until the late 2000s to see the first applications of adjoint-state methods in regional- and continental-scale earthquake seismology~\citep{tape2009adjoint,Fichtner09,zhu2012structure}.
The first global ``adjoint tomography'' model of the Earth's mantle,
GLAD-M15, was published in 2016~\citep{bozdaug2016global}, more than 30 years after the development of the original ``full waveform inversion'' (FWI) theory.

@@

Global adjoint tomography has a well-defined but complex workflow with multiple stages.
% including numerical simulations of synthetic seismograms (forward simulations) for all events,
% pre-processing of seismic data, making measurements, data assimilation, Fr\'echet derivative
% calculations (adjoint simulations), and post-processing of the gradient for quasi-Newton model
% updates.
It is essential to optimize, automate, and harden the entire process using workflow management tools, especially with large data sets.
In this study, for each iteration,
1,480 forward and adjoint simulations need to be performed (one pair for each earthquake in the database),
generating a few Petabytes of wavefield files for the parsimonious-storage kernel calculation algorithm of~\cite{KoXiBoPeSaLiTr16}, and consuming 16~million OLCF node hours.

@@

Fig.~\ref{fig:eventsstations}(a) shows a map of the 1,480 earthquakes
selected from the global Centroid-Moment Tensor (CMT) catalog~\citep[e.g.,][]{ekstrom2012global}
and used in this study.
To ensure a good signal-to-noise ratio on a global scale,
the smallest moment magnitude in the database is set to~5.5,
thereby capturing more deep events,
and, to avoid complications associated with source dimension and directivity,
the largest moment magnitude is set to~7.2.
Prior to the structural inversion,
we performed source inversions using model GLAD-M15 and the CMT inversion algorithm of \cite{liu2004spectral},
as described in the Supplementary Online Material (SOM).

@@

The seismographic stations used in this study are plotted in Fig.~\ref{fig:eventsstations}(b) and
were selected to optimize global coverage
and high data quality.
In addition to the seismographic  stations used for the source inversions,
we included available data for our 1,480 event earthquake database from many data centers,
including IRIS, ORFEUS, INGV, IPGP, ETH, and GEONET.
Regional and temporary networks,
such as US Array~(TA),
Africa Array~(AF), the Canadian National Seismograph Network~(CN), Geoscience Australia~(AU),
the Antarctic Seismographic Argentinean Italian Network~(AI), the New Zealand National Seismograph Network~(NZ), and the F-net broadband seismograph network by NIED, constitute a significant part
of our database and greatly improve coverage in certain regions.

@@

The misfit function to be minimized must
be carefully constructed.
Depending on the time window length and wave period range, we use a multi-taper technique \citep[e.g.,][]{laske_constraints_1996} to make frequency-dependent phase measurement when possible and adopt a cross-correlation measurement \citep[e.g.,][]{luo_wave-equation_1991} for the rest of data.
Measurements are made in several passbands of three-component seismograms rotated
into vertical, radial, and transverse components, resulting in a number of measurement
categories.
In this study, we consider four passbands, namely, a 17--40~s passband targeting body waves,
two 40--100~s passbands separately targeting body and surface waves,
and a 90--250~s passband targeting longer-period surface waves.
Each passband involves measurements on all three components,
which results in a total of twelve measurement categories.
Although the inversion is designed to minimize the overall misfit,
we track the misfit reduction in each of the categories to ensure that
the model is improving the fit to the data roughly equally.
One of the biggest challenges in the construction of the misfit function is the
highly uneven distribution of earthquakes and seismographic stations,
which must be counterbalanced by geographically weighting the data~\citep[e.g.][]{Li1996}.
This issue is discussed in detail by~\cite{Ruanetal2018};
in this section we present a brief synopsis.

@@

We observed misfit reductions in all categories,
with dispersive 40--100~s surface waves exhibiting the largest improvements.
The improvements in fit per component are comparable in all period bands,
indicating that the various categories are reasonably well balanced in the
assessment of misfit.

@@

Fig.~\ref{fig:M24-Iceland} showcases the north Atlantic, where we see clear expressions of the Jan Mayen and Iceland plumes as well as the Azores, Canary Islands, and Bermuda,
and Fig.~\ref{fig:M24-Reunion} shows the emergence of hotspots in the Indian Ocean in model GLAD-M25,
including Marion, Crozet, Kerguelen, and R\'eunion.
Visual inspection of the models reveals a significant increase in perturbation anomalies in GLAD-M25 compared to GLAD-M15,
which explains the misfit reductions in the histograms (Figs.~\ref{fig:phase_hist}~\&~\ref{fig:phase_hist_360}).

@@

Overall, the three models are in reasonably good agreement.
At shallow depths, model GLAD-M25 shows more distinct continental crust and cratons, thanks to the inclusion of surface waves.
But in the upper and mid mantle,
the models share similar attributes.

@@

@@

>>>>

Construction of the first seismic tomographic models of the Earth dates back to the late 1970s~\citep{Aki77,Dziewonski77,SenTok77} and early 1980s~\citep[e.g.,][]{WD84,Nataf1984}.
Around the same time,
\cite{BaChLa77}, \cite{Lailly1983}, and~\cite{Tar84} formulated and adapted the theory of adjoint-state methods~\citep{Chavent1974} for exploration seismology with the goal of capturing the full physics of seismic wave propagation.
Mainly due to computational challenges,
it took until the late 2000s to see the first applications of adjoint-state methods in regional- and continental-scale earthquake seismology~\citep[e.g.,][]{tape2009adjoint,Fichtner09,zhu2012structure}.
The first global ``adjoint tomography'' model of the Earth's mantle,
GLAD-M15, was published in 2016~\citep{bozdaug2016global}, more than 30 years after the development of the original ``full waveform inversion'' (FWI) theory.

@@

Global adjoint tomography has a well-defined but complex workflow with multiple stages.
% including numerical simulations of synthetic seismograms (forward simulations) for all events,
% pre-processing of seismic data, making measurements, data assimilation, Fr\'echet derivative
% calculations (adjoint simulations), and post-processing of the gradient for quasi-Newton model
% updates.
It is essential to optimize, automate, and harden the entire process using workflow management tools, especially with large data sets.
In this study, for each iteration,
1,480 forward and adjoint simulations need to be performed (one pair for each earthquake in the database),
generating a few Petabytes of wavefield files for the parsimonious-storage kernel calculation algorithm of~\cite{KoXiBoPeSaLiTr16}.

@@

Fig.~\ref{fig:eventsstations}(a) shows a map of the 1,480 earthquakes
selected from the global Centroid-Moment Tensor (CMT) catalog~\citep[e.g.,][]{ekstrom2012global}
within the moment magnitude range of $5.5 \leq M_w \leq 7.2$ used in this study.
To ensure a good coverage, specifically in the lower mantle, we incorporated data from
about 500 deep events, and, to avoid complications associated with source dimension and directivity,
the largest moment magnitude is set to~7.2.
Prior to the structural inversion,
we performed source inversions by computing Green's functions for the nine CMT source parameters (six moment tensor components, latitude, longitude, and depth) using model GLAD-M15 and the CMT inversion algorithm of~\cite{liu2004spectral},
as described in the Supplementary Online Material (SOM).

@@

The seismographic stations used in this study are plotted in Fig.~\ref{fig:eventsstations}(b) and
were selected to optimize global coverage
and high data quality.
%In addition to the seismographic  stations used for the source inversions,
We included available data from many data centers,
including IRIS, ORFEUS, INGV, IPGP, ETH, and GEONET.
Global Seismic Network (II, IU, IC, US, CU, and GT),
GEOFON~(GE), GEOSCOPE~(G), regional and temporary networks,
such as US Array~(TA),
Africa Array~(AF), the Canadian National Seismograph Network~(CN), Geoscience Australia~(AU),
the Antarctic Seismographic Argentinean Italian Network~(AI), the New Zealand National Seismograph Network~(NZ), and the F-net broadband seismograph network by NIED,  MedNet~(MN),
the Brazilian Lithospheric Seismic Project~(BL), the Chilean National Seismic Network~(C),
and the Japan Meteorological Agency Seismic Network~(JP) constitute a significant part
of our database and greatly improve coverage in certain regions.

@@

The misfit function to be minimized must
be carefully constructed, because it strongly affects the convergence of the inverse problem.
Depending on the time window length and wave period range, we use a multi-taper technique~\citep[e.g.,][]{laske_constraints_1996} to make frequency-dependent phase measurements to capture wave dispersion and adopt a cross-correlation measurement \citep[e.g.,][]{luo_wave-equation_1991} for non-dispersive waves.
Measurements are made in several passbands of three-component seismograms rotated
into vertical, radial, and transverse components, resulting in a number of measurement
categories.
In this study, we consider four passbands, namely, a 17--40~s passband targeting body waves,
two 40--100~s passbands separately targeting body and surface waves,
and a 90--250~s passband targeting longer-period surface waves.
Each passband involves measurements on all three components,
which results in a total of twelve measurement categories.
Although the inversion is designed to minimize the overall misfit,
we track the misfit reduction in each of the categories to ensure that
the model is improving the fit to the data roughly equally.
One of the biggest challenges in the construction of the misfit function is the
highly uneven distribution of earthquakes and seismographic stations,
which must be counterbalanced by geographically weighting the data~\citep[e.g.][]{Li1996}.
This issue is discussed in detail by~\cite{Ruanetal2018};
in this section we present a brief synopsis.

@@

We observe misfit reductions in all categories,
with dispersive 40--100~s surface waves exhibiting the largest improvements.
The improvements in fit per component are comparable in all period bands,
indicating that the various categories are reasonably well balanced in the
assessment of misfit.

@@

Fig.~\ref{fig:M24-Iceland} showcases the north Atlantic, where we see clear expressions of the Jan Mayen and Iceland plumes as well as the Azores, Canary Islands, and Bermuda,
and Fig.~\ref{fig:M24-Reunion} shows the emergence of hotspots in the Indian Ocean in model GLAD-M25,
including Marion, Crozet, Kerguelen, and R\'eunion.
Visual inspection of the models reveals a significant increase in perturbation anomalies in GLAD-M25 compared to GLAD-M15,
which explains the misfit reductions in the histograms (Figs.~\ref{fig:phase_hist}~\&~\ref{fig:phase_hist_360}).
More detailed comparisons between GLAD-M15 and GLAD-M25 are provided in the SOM.

@@

Overall, the three models are in reasonably good agreement.
At shallow depths, model GLAD-M25 shows more distinct continental crust and cratons, thanks to the inclusion of surface waves.
But in the upper and mid mantle,
the models share similar attributes.
The P-wave model of GLAD-M25 might be smoother than the other models due to a relatively longer minimum body-wave period (17~s).
Since there are fewer P- than S-wave measurements,
due to the smaller amplitudes of P waves, convergence of the P-wave model is likely to be slower than the S-wave model.

@@

Due to our cross-correlation measurements, smaller amplitude signals, such as higher-mode surface waves (which are crucial for imaging the mantle transition zone) and scattered waves (which illuminate plume features) may well be underrepresented in the current inversion.
Thus, there is still room for extracting more information from every time series by defining appropriate measurements to effectively incorporate smaller-amplitude signals~\citep[e.g.,][]{Bozdagetal2011,yuan_double-difference_2016}.

@@

After ten additional iterations,
GLAD-M25 shows a clear enhancement of plume and slab features compared to GLAD-M15 (see also the SOM).
It is promising to observe similarities between the P- and S-wavespeed models of GLAD-M25 and models from various other groups, while the remaining discrepancies need further investigation.
This highlights the importance of resolution and uncertainty quantification, which is one of the major challenges in seismic tomography.
Uncertainty quantification is an active area of research in FWI \cite[e.g.,][]{FivL2015,Fang2018,Thurin2019,Eikrem2019,Liu2019a,Liu2019b}, however, to date it has been challenging in practice, especially for large-scale inversions~\citep{Rawlinson2014}.

Our comparisons of different models largely focus on similarities of major patterns, such as plumes and slabs. Their shapes and depth  vary in detail, especially in the lithosphere, highlighting the importance of dealing with the crust properly in tomographic inversions.
Amplitudes of seismic models are required for thermochemical and geodynamical interpretations of the structure and dynamics of the mantle.
We observe a significant increase in the amplitude of GLAD-M25 compared to GLAD-M15 and other models.
Such an increase in amplitude is also evident in the models of~\cite{french2014whole,french2015broad}.
This illustrates the fact that the current generation of global models is no longer in the realm of linear perturbation theory.

### 2020-02-23 supplementary_material.tex
Updates from Overleaf

Instead of relying on crustal corrections,
the mesh implementation of the crust in the spectral-element solver SPECFEM3D\_GLOBE~\citep{KoTr02a,KoTr02b,PeKoLuMaLeCaLeMaLiBlNiBaTr11} enables us to accurately accommodate topography and bathymetry as well as variations in the Moho.
To improve the sampling of the thin oceanic crust the mesh honors the Moho whenever the crust is thinner than 15~km and thicker than 35~km. The mesh runs through the GLL (Gauss-Lobatto-Legendre) points at the ocean-continent transition (15--35~km crustal thickness) as described in \citet{tromp2010a}. The mantle and crust are inverted simultaneously,
thereby avoiding any simplifications or crustal corrections.

@@

To update the source parameters (six moment tensor components, latitude, longitude and depth) using the starting model to compute the Green's functions for each source parameter,
we used the CMT inversion algorithm of \cite{liu2004spectral}.
This algorithm combines a normalized waveform difference misfit with an envelope difference misfit.
Specifically, the algorithm minimizes the misfit function
\begin{equation}
   \begin{split}
      \Phi =  \sum\limits_{c=1}^{C} \omega_c \sum\limits_{r=1}^{R_c} \omega_{cr}
       \sum\limits_{w=1}^{W_{cr}} \omega_{crw}\,
          & \left\{ \lambda\, \frac
              { \int \big[ d_w(t) - s_w(t - \Delta t) \big]^2 \mathrm{d}t}
              {\int \big[ d_w(t) \big]^2  \mathrm{d}t} \right.
       \\ & \quad \left. \mbox{} + (1 - \lambda)\, \frac
              {\int \big[ e(d_w(t)) - e(s_w(t - \Delta t)) \big]^2 \mathrm{d}t}
              {\int \big[ e(d_w(t)) \big]^2\mathrm{d}t} \right\}
              \quad ,
   \end{split}
\end{equation}
where~$d_w(t)$ denotes data in time window~$w$\,,
and~$s_w(t - \Delta t)$ the corresponding synthetic for model~GLAD-M15.
We allow the synthetics to shift relative to the data by an amount~$\Delta t$
--- effectively a station correction --- determined by cross correlation. We do not invert for the origin times as we minimize the phase misfit due to the station correction, which helps to reduce the nonlinearity of the problem. As we describe later, we take into account the uncertainty in origin times, as well as the scalar moment, by performing an additional grid search at every iteration.
The envelope function is denoted by~$e(\,\cdot\,)$\,,
and the parameter~$\lambda$ determines the balance between fitting waveforms versus fitting envelopes.
The number of measurement categories is denoted by~$C$\,.
Following~\cite{ekstrom2012global},
seismograms were filtered between 50~s and 100~s
to select three-component body-wave windows,
and between 60~s and 100~s to select three-component
surface-wave windows,
resulting in six measurement categories, $c=1,\ldots,C$\,.
To balance their contributions,
each category is weighted by the reciprocal of the number of measurements in that
category, $\omega_c$\,.
The number of windows for a given receiver~$r$ in a given measurement category~$c$ is~$W_{cr}$\,.
Each such window is weighted equally, i.e.,~$\omega_{crw}=1$\,.
The number of receivers that records data in category~$c$ is denoted by~$R_c$\,.
As shown in Fig.~\ref{fig:source_correction}b,
the receivers are unevenly distributed across the globe,
with several dense arrays in the northern hemisphere and poor coverage in the southern hemisphere.
To balance the coverage,
following a strategy articulated by~\cite{Ruanetal2018},
we assign receiver weights~$\omega_{cr}$ based on the expression
\begin{equation}
\omega_{cr}^{-1} = N_c\,\sum_{r'=1}^{R_c} \exp\left[\mbox{}-\left(\frac{\Delta_{rr'}}{\Delta_c}\right)^2\right]
\quad ,
\label{eq:spatial_weights}
\end{equation}
where~$N_c$ is a normalization factor for category~$c$,
and where~$\Delta_{rr'}$ denotes the angular distance between receivers~$r$ and~$r'$\,.
The reference angular distance~$\Delta_c$ for each category~$c$ needs to be chosen such that the condition 
number of the diagonal weighting matrix defined by Eqn.~(\ref{eq:spatial_weights}) is not too large.
The calculation of the weights may be abstracted as: given a distribution of
points on the unit sphere, determine a spatial weighting associated with each point.

@@

Most earthquakes, specifically oceanic ridge events, are shallower after inversion
(Fig.~\ref{fig:source_correction}c),
consistent with our previous experiences~\citep[e.g.,][]{zhu2015seismic,chen2015multiparameter,bozdaug2016global} and with experiments by~\cite{hjorleifsdottir2010effects}. This is partly because the minimum depth of CMT events is fixed to $\sim12$~km, because the sensitivity of source parameters significantly decreases closer to the free surface. 
We observed an average depth change of~$-2.62\pm2.49$~km relative to the global CMT solutions,
an average scalar moment change of~$5.31\pm3.91$\%,
and an average centroid time shift of~$-0.60\pm1.17$~s.
These are relatively minor corrections, mainly due to being conservative in the source inversions to avoid nonlinearities and the not-so-detailed crustal model (an updated version of CRUST2.0 through the 15 iterations performed for GLAD-M15), especially in view of the significant expense of the source inversions.
For this reason, when we added another 440 earthquakes during iteration~22,
thereby bringing the total to~1,480 events,
we only performed a grid search to calibrate the centroid times and scalar moments.

@@

The postprocessing stage of the workflow takes Fr\'echet derivatives as input and
generates a model update as output.
It involves the following steps.
\begin{enumerate}
  \item Summation of the individual Fr\'echet derivatives for each earthquake, called ``event kernels", to obtain the overall gradient of the misfit function. The contribution of each source is weighted to balance
    the uneven distribution of earthquakes~\citep{Ruanetal2018}.
  \item Smoothing of the raw misfit gradient using a 3D Gaussian, which
    serves as a regularization procedure. Instead of using a changing
    smoothing radius based upon the ``kernel density''~\citep{bozdaug2016global},
    we used a fixed value at a given iteration, following~\cite{zhu2012structure}. One can also combine source-receiver weighting with the multi-stage smoothing strategy to highlight structure underneath densely covered regions, as in~\citet{bozdaug2016global}.
  \item Preconditioning of the smoothed gradient based on a technique proposed by~\cite{luo2013strategies}.
  \item Line search in the direction of the negative gradient to determine the magnitude of the model update.
  The search direction is determined using a nonlinear conjugate gradient method (iterations 16--21) or a Limited-memory Broyden- Fletcher-Goldfarb-Shanno (L-BFGS) quasi-Newton method (iterations 22--25)~\citep{wright1999numerical}.
  We used a subset of 160 earthquakes to conduct the line search and determine the step length. One can also determine the step length using the Wolf criteria, which are commonly used in exploration studies \cyan{reference}. We prefer to perform the line search to be able to keep track of the evolution of the misfit in every measurement category.
\end{enumerate}

@@

This section summarizes the complete Point Spread Function (PSF) tests conducted as part of this study, including the tradeoff between parameters.
Figs.~\ref{fig:psf_yellowstone}--\ref{fig:psf_usa_east} show the results of PSF tests underneath Yellowstone, Easter Island, Afar, ,Sumatra and two extra locations in United States..
Each figure shows the original Gaussian perturbation in vertically polarized shear wavespeed, $\mathsf{\Delta}\mathsf{m}$\,, in map view and cross section, as well as the action of the Hessian on this model perturbation, $\mathsf{H}\mathsf{\Delta}\mathsf{m}$\,.

We used different sized Gaussian perturbations in the PSF tests, from 160~to~400~km in diameter depending on the kernel coverage of the selected regions, both in the upper and lower mantle. Although we observe some smearing effects, the Gaussian anomalies are overall well-recovered. As expected, PSF tests are most successful in North America, where we have the best coverage, thanks to USArray. However, it is also encouraging to see good recovery in the lower mantle to assess the resolution of lower-mantle plumes. We observe limited smearing onto other parameters, e.g., we observe a slight tradeoff in radial anisotropy in the upper mantle for the tests performed underneath North America.

>>>>

Instead of relying on crustal corrections,
the mesh implementation of the crust in the spectral-element solver SPECFEM3D\_GLOBE~\citep{KoTr02a,KoTr02b,PeKoLuMaLeCaLeMaLiBlNiBaTr11} enables us to accurately accommodate topography and bathymetry as well as variations in the Moho.
To improve sampling of the thin oceanic crust, the mesh honors the Moho whenever the crust is thinner than 15~km and thicker than 35~km. The mesh runs through the Gauss-Lobatto-Legendre points at the ocean-continent transition (15--35~km crustal thickness) as described in \citet{tromp2010a}. The mantle and crust are inverted simultaneously,
thereby avoiding any simplifications or crustal corrections.

@@

To update the source parameters (six moment tensor components, latitude, longitude and depth) using the starting model to compute the Green's functions for each source parameter,
we used the CMT inversion algorithm of \cite{liu2004spectral}.
This algorithm combines a normalized waveform difference misfit with an envelope difference misfit.
Specifically, the algorithm minimizes the misfit function
\begin{equation}
   \begin{split}
      \Phi =  \sum\limits_{c=1}^{C} \omega_c \sum\limits_{r=1}^{R_c} \omega_{cr}
       \sum\limits_{w=1}^{W_{cr}} \omega_{crw}\,
          & \left\{ \lambda\, \frac
              { \int \big[ d_w(t) - s_w(t - \Delta t) \big]^2 \mathrm{d}t}
              {\int \big[ d_w(t) \big]^2  \mathrm{d}t} \right.
       \\ & \quad \left. \mbox{} + (1 - \lambda)\, \frac
              {\int \big[ e(d_w(t)) - e(s_w(t - \Delta t)) \big]^2 \mathrm{d}t}
              {\int \big[ e(d_w(t)) \big]^2\mathrm{d}t} \right\}
              \quad ,
   \end{split}
\end{equation}
where~$d_w(t)$ denotes data in time window~$w$\,,
and~$s_w(t - \Delta t)$ the corresponding synthetic for model~GLAD-M15.
We allow the synthetics to shift relative to the data by an amount~$\Delta t$
--- effectively a station correction --- determined by cross correlation. We do not invert for the origin times as we minimize the phase misfit due to the station correction, which helps to reduce the nonlinearity of the problem.
As described later, we take into account uncertainties in the centroid time and scalar moment by performing an additional grid search at the start of every iteration.
The envelope function is denoted by~$e(\,\cdot\,)$\,,
and the parameter~$\lambda$ determines the balance between fitting waveforms versus fitting envelopes.
The number of measurement categories is denoted by~$C$\,.
Following~\cite{ekstrom2012global},
seismograms were filtered between 50~s and 100~s
to select three-component body-wave windows,
and between 60~s and 100~s to select three-component
surface-wave windows,
resulting in six measurement categories, $c=1,\ldots,C$\,.
To balance their contributions,
each category is weighted by the reciprocal of the number of measurements in that
category, $\omega_c$\,.
The number of windows for a given receiver~$r$ in a given measurement category~$c$ is~$W_{cr}$\,.
Each such window is weighted equally, i.e.,~$\omega_{crw}=1$\,.
The number of receivers that records data in category~$c$ is denoted by~$R_c$\,.
As shown in Fig.~\ref{fig:source_correction}b,
the receivers are unevenly distributed across the globe,
with several dense arrays in the northern hemisphere and poor coverage in the southern hemisphere.
To balance the coverage,
following a strategy articulated by~\cite{Ruanetal2018},
we assign receiver weights~$\omega_{cr}$ based on the expression
\begin{equation}
\omega_{cr}^{-1} = N_c\,\sum_{r'=1}^{R_c} \exp\left[\mbox{}-\left(\frac{\Delta_{rr'}}{\Delta_c}\right)^2\right]
\quad ,
\label{eq:spatial_weights}
\end{equation}
where~$N_c$ is a normalization factor for category~$c$,
and where~$\Delta_{rr'}$ denotes the angular distance between receivers~$r$ and~$r'$\,.
The reference angular distance~$\Delta_c$ for each category~$c$ needs to be chosen such that the condition 
number of the diagonal weighting matrix defined by Eqn.~(\ref{eq:spatial_weights}) is not too large.
The calculation of the weights may be abstracted as: given a distribution of
points on the unit sphere, determine a spatial weighting associated with each point.

@@

Most earthquakes, specifically oceanic ridge events, are shallower after inversion
(Fig.~\ref{fig:source_correction}c),
consistent with our previous experiences~\citep[e.g.,][]{zhu2015seismic,chen2015multiparameter,bozdaug2016global} and with experiments by~\cite{hjorleifsdottir2010effects}. This is partly because the minimum depth of CMT events is fixed to $\sim12$~km, because the sensitivity of source parameters is significantly reduced closer to the free surface. 
We observed an average depth change of~$-2.62\pm2.49$~km relative to the global CMT solutions,
an average scalar moment change of~$5.31\pm3.91$\%,
and an average centroid time shift of~$-0.60\pm1.17$~s.
These are relatively minor corrections, mainly due to being conservative in the source inversions to avoid nonlinearities and the not-so-detailed crustal model (an updated version of CRUST2.0 as a result of the 15 iterations performed for GLAD-M15), especially in view of the significant expense of the source inversions.
For this reason, when we added another 440 earthquakes during iteration~22,
thereby bringing the total to~1,480 events,
we only performed a grid search to calibrate the centroid times and scalar moments.

@@

The postprocessing stage of the workflow takes Fr\'echet derivatives as input and
generates a model update as output.
It involves the following steps.
\begin{enumerate}
  \item Summation of the individual Fr\'echet derivatives for each earthquake, called ``event kernels", to obtain the overall gradient of the misfit function. The contribution of each source is weighted to balance
    the uneven distribution of earthquakes~\citep{Ruanetal2018}.
  \item Smoothing of the raw misfit gradient using a 3D Gaussian, which
    serves as a regularization procedure. Instead of using a changing
    smoothing radius based upon the ``kernel density''~\citep{bozdaug2016global},
    we used a fixed value at a given iteration, following~\cite{zhu2012structure}. One can also combine source-receiver weighting with the multi-stage smoothing strategy to highlight structure underneath densely covered regions, as in~\citet{bozdaug2016global}.
  \item Preconditioning of the smoothed gradient based on a technique proposed by~\cite{luo2013strategies}.
  \item Line search in the direction of the negative gradient to determine the magnitude of the model update.
  The search direction is determined using a nonlinear conjugate gradient method (iterations 16--21) or a Limited-memory Broyden- Fletcher-Goldfarb-Shanno (L-BFGS) quasi-Newton method (iterations 22--25)~\citep{wright1999numerical,NoWr06}.
  We used a subset of 160 earthquakes to conduct the line search and determine the step length.
  One can also determine the step length using the Wolfe criteria, which are commonly used in exploration studies~\citep{NoWr06}. We prefer to perform the line search to be able to keep track of the evolution of the misfit in every measurement category.
\end{enumerate}

@@

This section summarizes the complete Point Spread Function (PSF) tests conducted as part of this study, including the tradeoff between parameters.
Figs.~\ref{fig:psf_yellowstone}--\ref{fig:psf_usa_east} show the results of PSF tests underneath Yellowstone, Easter Island, Afar, ,Sumatra and two additional locations in United States..
Each figure shows the original Gaussian perturbation in vertically polarized shear wavespeed, $\mathsf{\Delta}\mathsf{m}$\,, in map view and cross section, as well as the action of the Hessian on this model perturbation, $\mathsf{H}\mathsf{\Delta}\mathsf{m}$\,.

We used different sized Gaussian perturbations in the PSF tests, from 160~to~400~km in diameter depending on the kernel coverage of the selected regions, both in the upper and lower mantle. Although we observe some smearing effects, the Gaussian anomalies are overall well-recovered.
As expected, our PSF tests are most successful in North America, where we have the best coverage, thanks to USArray. However, it is also encouraging to see good recovery in the lower mantle to assess the resolution of lower-mantle plumes. We observe limited smearing onto other parameters, e.g., we observe a slight tradeoff in radial anisotropy in the upper mantle for the tests performed underneath North America.
